Chlorophylla

### 2019-02-28 Chlorophyll_a .Rmd
fixed

ggplot(daily_chloro_data, aes(x = date, y = chloro)) +
  geom_line() +
  facet_wrap(~combi, ncol = 1)

>>>>

#Plotting daily data
ggplot(daily_chloro_data, aes(x = date, y = chloro)) +
  geom_line() +
  facet_wrap(~combi, ncol = 1)

# Plotting only years 2014-2015
daily_chloro_data_tester <- daily_chloro_data %>% 
  filter(year(date) %in% seq(2014, 2015))

ggplot(daily_chloro_data_tester, aes(x = date, y = chloro)) +
  geom_line() +
  facet_wrap(~combi, ncol = 1)
